Indirect Conflicts: An Exploration and Discussion of Tools, Process, and Developer Insight

### 2013-08-29 iced-2013/paper.tex
Added abstract.

\usepackage{enumitem}

\setlist[description]{leftmargin=*}
\floatstyle{plaintop}
\restylefloat{table}

@@

\begin{abstract}

@@

\begin{description}[topsep=6pt]
	\item[RQ1] \textit{How do indirect conflicts occur?}
\end{description}

@@

\begin{description}[topsep=6pt]
	\item[RQ2] \textit{How often do indirect conflicts occur and at what times in a project do they occur more frequently?}
\end{description}

@@

\begin{description}[topsep=6pt]
	\item[RQ3] \textit{What software artifacts and environments are susceptible to indirect conflicts?}
\end{description}

@@

\begin{description}[topsep=6pt]
	\item[RQ4] \textit{How do developers catch indirect conflicts?}
\end{description}

@@

\begin{description}[topsep=6pt]
	\item[RQ5] \textit{How to developers react to and solve indirect conflicts?}
\end{description}

@@

\begin{description}[topsep=6pt]
	\item[RQ6] \textit{When are pre-emptive indirect conflict tools best used and what would developers want from them?}
\end{description}

@@

\begin{description}[topsep=6pt]
	\item[RQ7] \textit{What kinds of tools do developers want to help them handle and solve indirect conflicts?}
\end{description}

>>>>

\floatstyle{plaintop}
\restylefloat{table}

@@

\begin{abstract}
Developer awareness techniques have been proposed and studied to aid in developer
understanding and  efficient developer output in terms of source code produced. These techniques
involve the sharing of information regarding source code changes in a specific project in order
to either catch potential issues before they are fully integrated or to help developers debug
pre-existing issues. These techniques have largely focused on either \textit{direct} or 
\textit{indirect conflict} issues. While the techniques and tools for direct conflicts have had
large success, tools either proposed or studied which focus on indirect conflicts have had many common
struggles and poor developer interest. To better understand why indirect conflict tools either fail or have little
developer investment, we performed a grounded theory study with 97 developers involved in either
interviews or a web survey. We identified the main features that characterize indirect conflict issues,
what processes and techniques developers use to aid in preventing and solving indirect conflict issues,
and what developers would look for in a tool to aid them in these conflicts.

@@

\begin{description}
	\item[RQ1] \textit{How do indirect conflicts occur?}
\end{description}

@@

\begin{description}
	\item[RQ2] \textit{How often do indirect conflicts occur and at what times in a project do they occur more frequently?}
\end{description}

@@

\begin{description}
	\item[RQ3] \textit{What software artifacts and environments are susceptible to indirect conflicts?}
\end{description}

@@

\begin{description}
	\item[RQ4] \textit{How do developers catch indirect conflicts?}
\end{description}

@@

\begin{description}
	\item[RQ5] \textit{How to developers react to and solve indirect conflicts?}
\end{description}

@@

\begin{description}
	\item[RQ6] \textit{When are pre-emptive indirect conflict tools best used and what would developers want from them?}
\end{description}

@@

\begin{description}
	\item[RQ7] \textit{What kinds of tools do developers want to help them handle and solve indirect conflicts?}
\end{description}
